---
title: "Homework Exercise 1"
author: "W203 Instructional Team"
date: ""
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

W203 Statistics for Data Science
========================================================
Unit 1 Homework
========================================================


Load the dataset found in the file, cars.csv.

Load dataset into a data frame Cars.
```{r load}
setwd("/Users/jayz/Downloads/homework1")
Cars <- read.table("cars.csv", sep=",", header=TRUE)
```


1. What are the variables in the file?

Variables in file are: mpg, cyl, disp, hp, drat, wt, qsec, vs, am, gear, carb
```{r}
 names(Cars)
```


2. Find the mean, median, minimum, maximum, 1st quartile and 3rd quartile for the mpg variable.

Mean is        : 19.492
Median is      : 18.7
Minimum is     : 10.4
Maximum is     : 33.9
1st Quantile is: 15.2
3rd Quantile is: 21.5
```{r}
 mean(Cars$mpg)
 median(Cars$mpg)
 min(Cars$mpg)
 max(Cars$mpg)
 quantile(Cars$mpg, probs=c(.25, .75))
```


3. Create a histogram of the mpg variable. 

```{r}
 hist(Cars$mpg, main="Car mpg histogram", xlab="mpg")
```


4. What is the standard deviation of mpg variable?

Standard deviation is: 6.047446

```{r}
 sd(Cars$mpg)
```


5. What is the variance of mpg variable?

Variance is: 36.5716 

```{r}
 var(Cars$mpg)
```

6. What is the relationship of the standard deviation to the variance? Why does the standard deviation and variance of the mpg variable differ? 

Standard deviation is the square root of the variance, which explains their difference.
```{r}
 sd(Cars$mpg)
 var(Cars$mpg)
 sqrt(var(Cars$mpg))
```


7. How many data points are there for the cyl variable? 

There are 25 data points in Cars$cyl, 2 of which have missing values.
```{r}
 str(Cars$cyl)
 summary(Cars$cyl)
```

8. What is the mean of the cyl variable?

Mean of cyl is 6.26087
```{r}
 mean(Cars$cyl, na.rm=TRUE)
```
